---
title: "MetaPR2 - Figures Machine Learning"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---


# Initialize

```{r init, echo=TRUE, message=FALSE, warning=FALSE}
source(here::here("R", "init.R"))
```

# Figures

## Parameters

```{r}
cluster_asv = TRUE
protist_only = TRUE
```



## V4 - protists - DNA


```{r}

division_memoved <- c()

if (protist_only) {
division_memoved <- c("Metazoa", "Fungi", "Streptophyta")
}

asv_set_V4 <- list()

if (cluster_asv) {
  asv_set_V4$df <- asv_set$df_cluster 
} else {
  asv_set_V4$df <- asv_set$df 
}

asv_set_V4$df <- asv_set_V4$df %>% 
  dplyr::filter(gene_region == "V4", 
                DNA_RNA == "DNA",
                !(division %in% division_memoved))

n_reads_pct_V4 <- sum(asv_set_V4$df$n_reads_pct)
n_reads_V4 <- sum(asv_set_V4$df$n_reads)

samples_V4 <- asv_set_V4$df %>% 
  pull("file_code") %>% 
  unique()

n_samples_V4 <- length(samples_V4)

sampling_sites_V4 <- asv_set_V4$df %>%
  select(latitude, longitude) %>% 
  distinct()

n_sampling_sites_V4 <- nrow(sampling_sites_V4)
  
asv_code_V4 <- asv_set_V4$df %>% 
  dplyr::filter(gene_region == "V4", 
                DNA_RNA == "DNA",
                !(division %in% division_memoved)) %>% 
  pull("asv_code") %>% 
  unique()

asv_set_V4$fasta <- asv_set$fasta %>% 
  filter(asv_code %in% asv_code_V4)

asv_set_V4$samples <- asv_set$samples %>% 
  filter(file_code %in% asv_set_V4$df$file_code)

n_asvs_V4 <- nrow(asv_set_V4$fasta)

cat("Total numbers of V4 samples: ",n_samples_V4, "\n" )
cat("Total numbers of V4 sampling sites: ",n_sampling_sites_V4, "\n" )
cat("Total numbers of V4 ASVs: ",n_asvs_V4 , "\n")
cat("Total numbers of V4 reads: ", formatC(n_reads_V4,big.mark = " ") , "\n" )
```

# Testing mikropml

```{r}
library(mikropml)

otu_mini_bin

# results <- run_ml(otu_mini_bin,
#   'glmnet',
#   outcome_colname = 'dx',
#   seed = 2019)

```


# Testing on a subset of the table

```{r}

ml <- asv_set_V4$df %>% 
  filter(dataset_id %in% c(1,205), 
         class == "Mamiellophyceae") %>% 
  select(asv_code, species, file_code, dataset_code, n_reads, ecosystem) %>% 
  mutate(asv_code = str_c(asv_code, species, sep = "_"),
         file_code = str_c(file_code, dataset_code, sep = "_"),
         ecosystem = as.character(ecosystem)) %>% 
  select(-species, -dataset_code) %>% 
  pivot_wider(names_from = asv_code, values_from = n_reads, values_fill = 0) %>% 
  select(-file_code)

qs::qsave(ml, here("data", "ml_sample_V4_clust.qs"))

preprocessed <- preprocess_data(dataset = ml, outcome_colname = "ecosystem") 



ml <- preprocessed$dat_transformed

results_glmnet <- run_ml(ml,
  'glmnet',
  outcome_colname = 'ecosystem',
  find_feature_importance = TRUE,
  seed = 2019)

results_glmnet$feature_importance
  
results_rf <- run_ml(ml,
  'rf',
  outcome_colname = 'ecosystem',
  find_feature_importance = TRUE,
  seed = 2019)

results_rf$feature_importance

results_xgb <- run_ml(ml,
  'xgbTree',
  outcome_colname = 'ecosystem',
  find_feature_importance = TRUE,
  seed = 2019)

results_xgb$feature_importance

```

# Testing on the whole dataset with reads number

## Save matrix

```{r}

ml <- asv_set_V4$df %>% 
  # filter(dataset_id %in% c(1,205), 
  #        class == "Mamiellophyceae") %>% 
  select(asv_code, species, file_code, dataset_code, n_reads, ecosystem) %>% 
  mutate(asv_code = str_c(asv_code, species, sep = "_"),
         file_code = str_c(file_code, dataset_code, sep = "_"),
         ecosystem = as.character(ecosystem)) %>% 
  select(-species, -dataset_code) %>% 
  pivot_wider(names_from = asv_code, values_from = n_reads, values_fill = 0) %>% 
  select(-file_code)

qs::qsave(ml, here("data", "ml_V4_clust.qs"))

```


##  Results

Run on Roscoff server

# GLM: 
AUC = 0.82
feature_importance
-0.0891461776133018	89da934611_Dino-Group-I-Clade-1_X_sp.

# RF: 
AUC = 0.73
feature_importance
0.658572776162147	537e3642a2_Gymnodinium_sp.

```{r}

preprocessed <- qs::qread(here("data", "ml_V4_clust.preprocessed.qs"))


results_glm <- qs::qread(here("data", "ml_V4_clust.results_glm.qs"))

results_glm$performance
DT::datatable(results_glm$feature_importance)

results_rf <- qs::qread(here("data", "ml_V4_clust.results_rf.qs"))

results_rf$performance
DT::datatable(results_rf$feature_importance)

```
# Testing on the whole dataset with reads pct

## Save matrix

```{r}

ml <- asv_set_V4$df %>% 
  # filter(dataset_id %in% c(1,205), 
  #        class == "Mamiellophyceae") %>% 
  select(asv_code, species, file_code, dataset_code, n_reads_pct, ecosystem) %>% 
  mutate(asv_code = str_c(asv_code, species, sep = "_"),
         file_code = str_c(file_code, dataset_code, sep = "_"),
         ecosystem = as.character(ecosystem)) %>% 
  select(-species, -dataset_code) %>% 
  pivot_wider(names_from = asv_code, values_from = n_reads_pct, values_fill = 0) %>% 
  select(-file_code)

qs::qsave(ml, here("data", "ml_V4_clust_pct.qs"))

```


##  Results

Run on Roscoff server

# GLM: 
AUC = **0.92**
feature_importance
-0.0860235238009247	250ae5aabd_Dino-Group-I-Clade-1_X_sp.

# RF: 
AUC = 0.857
feature_importance
0.491024060376396	537e3642a2_Gymnodinium_sp.


```{r}

preprocessed <- qs::qread(here("data", "ml_V4_clust_pct.preprocessed.qs"))


results_glm <- qs::qread(here("data", "ml_V4_clust_pct.results_glm.qs"))

results_glm$performance

DT::datatable(results_glm$feature_importance)

results_rf <- qs::qread(here("data", "ml_V4_clust_pct.results_rf.qs"))

results_rf$performance

DT::datatable(results_rf$feature_importance)

```
